---
title             : "Exploring Dwell Times for Dynamic Fractals"
shorttitle        : "Fractal Dwell Times"

author: 
  - name          : "Scott Wallner"
    affiliation   : "1, 2"
    corresponding : no    # Define only one corresponding author
    email         : "swallner@uoregon.edu"
  - name          : "Tess Sameshima"
    affiliation   : "1, 2"
    email         : "tesufuai@uoregon.edu"
  - name          : "Benjamin Chaloupka"
    affiliation   : "1, 2"
    email         : "bchaloup@uoregon.edu"

affiliation:
  - id            : "1"
    institution   : "University of Oregon"
  - id            : "2"
    institution   : "Institute of Oregon"

authornote: |
  Perception and Action Lab, Cognitivie Dynamics Lab, & Brain and Memory Lab

abstract: |
  Our primary research question is whether dwell times systematically differ between growth and decay sequences. We will examine this question both within and across subjects. Additionally, we are possibly interested in several exploratory analyses. For example, do specific fractal images elicit longer dwell times? Do specific levels of complexity elicit longer dwell times? Is there a dwell time pattern when fractal iterations are presented randomly? Does dwell time systematically decrease over time (if so, we may need to normalize dwell times to account for this)?
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "fractals, dwell times, growth and decay sequences"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(fig.width = 6.5,
                      fig.height = 8,
                      echo = F,
                      warning = F,
                      message = F)

library("papaja")
library(here)
library(rio)
library(janitor)
library(tidyverse)

theme_set(theme_minimal())
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r load data, include=FALSE}
data81 <- import(here("data", "star.csv"))
```

@brazhe2006self say stuff about fractals and such. Another group of researchers does too [@lowen1993fractal].

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

```{r}
data81 %>% 
  group_by(sex, frl) %>% 
  summarise(math_mean = round(mean(tmathss), 2), math_sd = round(sd(tmathss), 2), rdg_mean = round(mean(treadss), 2), rdg_sd = round(sd(treadss), 2)) %>% 
  knitr::kable()
```

Girls who paid for their lunches had the highest reading and math scores on average. In both boys and girls, students who get free lunch scored lower in both math and reading.

```{r}
data81 %>% 
  ggplot(aes(x = totexp, y = tmathss)) +
  geom_point(color = "gray42") +
  geom_smooth(aes(color = frl), method = "lm") +
  labs(x = "Teacher Experience (years)", y = "Total Math Scale Score", title = "Relation between teacher experience and math scores", subtitle = "Separate regression lines displayed by free/reduced price lunch status", color = "Lunch status") +
  theme(legend.position="bottom") +
  scale_color_discrete(labels = c("Paid Meals", "Free/Reduced Price Meals"))
```

On average, students who paid for their meals had a higher overall total math score.  It does not seem that teacher experience has a strong effect on total math score.  Perhaps the difference between paid or free meals relates to the students' SES which has an effect on total math score.

# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
